Accelerating Precision Medicine with Quantum Computing and AI\\\bigskip \LARGE\mdseries\itshape\color{black!80} Exploring the future of Personalized Health Care\par

### 2022-01-24 paper.tex
(paper) add frontend information

% Created 2022-01-23 Sun 17:09
% Intended LaTeX compiler: pdflatex
\documentclass{scrartcl}
\renewcommand\sectionformat{\llap{\thesection\autodot\enskip}}
\renewcommand\subsectionformat{\llap{\thesubsection\autodot\enskip}}
\renewcommand\subsubsectionformat{\llap{\thesubsubsection\autodot\enskip}}

@@

\author{Shaurya Singh, Abrahim Mahmud}
\date{\today}
\title{Accelerating Precision Medicine with Quantum Computing and AI\\\bigskip
\LARGE\mdseries\itshape\color{black!80} Exploring the future of Personalized Health Care\par}
\colorlet{greenyblue}{blue!70!green}
\colorlet{blueygreen}{blue!40!green}
\providecolor{link}{named}{greenyblue}
\providecolor{cite}{named}{blueygreen}
\hypersetup{
  pdfauthor={Shaurya Singh, Abrahim Mahmud},
  pdftitle={Accelerating Precision Medicine with Quantum Computing and AI},
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 29.0.50 (Org mode 9.6)},
  pdflang={English},
  breaklinks=true,
  colorlinks=true,
  linkcolor=,
  urlcolor=link,
  citecolor=cite
}
\urlstyle{same}
\makeatletter
\newcommand{\citeprocitem}[2]{\hyper@linkstart{cite}{citeproc_bib_item_#1}#2\hyper@linkend}
\makeatother

@@

\section{Introduction}
\label{sec:org24418c2}

@@

\section{AI in Precision Medicine}
\label{sec:orgb691230}

@@

\subsection{Accelerating AI with Quantum Computing}
\label{sec:org00dd5e6}

@@

\subsection{Hybrid Quantum-Classical Neural Networks}
\label{sec:orgfd6028d}

@@

\subsection{Generative Adversarial Networks}
\label{sec:org8cd7720}

@@

\subsubsection{MolGAN}
\label{sec:orgca00779}

@@

\subsubsection{Qubit-efficient Quantum Molecule Generation}
\label{sec:org47df466}

@@

\section{Prototype}
\label{sec:org97fa9db}

@@

\subsection{Image recognition (QuTorch-HG)}
\label{sec:org15b0f9e}

@@

\subsection{Quantum Accelerated Drug \& Molecule Generation (QGAN-HG)}
\label{sec:org4d44918}

@@

\subsection{Data}
\label{sec:orge4e24ff}

@@

\subsection{Tools and Hardware}
\label{sec:org702d6db}

@@

Code is developed in Jupyter notebooks allowing for quick prototyping, and utilize PyTorch for pre-processing and post-processing of our neural network, taking advantage of GPU Acceleration via Nvidia CUDA if available. This allows us to process images in real time on Google's Compute Engine VM's via Google Colab, allowing for low operating costs, high performance, and good portability.

@@

\section{Results}
\label{sec:org83bd39f}

\subsection{Speed}
\label{sec:orgd088ab6}

@@

\subsection{Accuracy}
\label{sec:org6d3f062}

@@

\subsection{Pricing}
\label{sec:org4368166}

@@

\section{Conclusion and Further Research}
\label{sec:org63bacf7}

@@

\section{References}
\label{sec:org5f0dea7}

>>>>

% Created 2022-01-23 Sun 19:46
% Intended LaTeX compiler: pdflatex
\documentclass{scrartcl}
\renewcommand\sectionformat{\llap{\thesection\autodot\enskip}}
\renewcommand\subsectionformat{\llap{\thesubsection\autodot\enskip}}
\renewcommand\subsubsectionformat{\llap{\thesubsubsection\autodot\enskip}}

@@

\author{Shaurya Singh}
\date{\today}
\title{Accelerating Precision Medicine with Quantum Computing and AI\\\bigskip
\LARGE\mdseries\itshape\color{black!80} Exploring the future of Personalized Health Care\par}
\colorlet{greenyblue}{blue!70!green}
\colorlet{blueygreen}{blue!40!green}
\providecolor{link}{named}{greenyblue}
\providecolor{cite}{named}{blueygreen}
\hypersetup{
  pdfauthor={Shaurya Singh},
  pdftitle={Accelerating Precision Medicine with Quantum Computing and AI},
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 29.0.50 (Org mode 9.6)},
  pdflang={English},
  breaklinks=true,
  colorlinks=true,
  linkcolor=,
  urlcolor=link,
  citecolor=cite
}
\urlstyle{same}
\makeatletter
\newcommand{\citeprocitem}[2]{\hyper@linkstart{cite}{citeproc_bib_item_#1}#2\hyper@linkend}
\makeatother

@@

\section{Introduction}
\label{sec:org39f930d}

@@

\section{AI in Precision Medicine}
\label{sec:org6f18950}

@@

\subsection{Accelerating AI with Quantum Computing}
\label{sec:org698183d}

@@

\subsection{Hybrid Quantum-Classical Neural Networks}
\label{sec:org22eb2fb}

@@

\subsection{Generative Adversarial Networks}
\label{sec:org5b0ecef}

@@

\subsubsection{MolGAN}
\label{sec:org427ddc7}

@@

\subsubsection{Qubit-efficient Quantum Molecule Generation}
\label{sec:orgb9a908b}

@@

\section{Prototype}
\label{sec:org203ee70}

@@

\subsection{Image recognition (QuTorch-HG)}
\label{sec:org02d8383}

@@

\subsection{Quantum Accelerated Drug \& Molecule Generation (QGAN-HG)}
\label{sec:org33edf53}

@@

\subsection{Data}
\label{sec:org3477476}

@@

\subsection{Tools and Hardware}
\label{sec:orgeb8e564}

@@

Code is developed in emacs' org-mode, combined with Jupyter kernels allowing for quick prototyping, and utilize PyTorch for pre-processing and post-processing of our neural network, taking advantage of GPU Acceleration via Nvidia CUDA if available. This allows us to process images in real time on Google's Compute Engine VM's via Google Colab, allowing for low operating costs, high performance, and good portability. Org-Mode allows us to document our code and easily integrate with other languages, while staying in a simple plain text format.

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./assets/literatejupyter.png}
\caption{\textbf{Jupyter in Org-Mode}}
\end{figure}

@@

\section{Results}
\label{sec:orge9f3984}

\subsection{Speed}
\label{sec:org5a6f58b}

@@

\subsection{Accuracy}
\label{sec:orgea680da}

@@

\subsection{Pricing}
\label{sec:org1362d9f}

@@

\subsection{Frontend}
\label{sec:orga20beeb}

In order to provide users an easy interface to collect and store their data, we created a Frontend written in React. Through React, we created a website that can collect crucial information, display user data, as well as ensure each user has their data easily accessible and protected through a database managed on firestore, backed up Google's OAuth authentication. Each user can view their likely hood for rare diseases, can document any symptoms or issues they're experiencing, talk with a live doctor, and analyze XRAY-scans.

The full code for both notebooks are available under \href{frontend/}{the frontend folder}.

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./assets/QML-PM_LOGIN.png}
\caption{\textbf{Google Login with Firebase}}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./assets/QML-PM_DASHBOARD.png}
\caption{\textbf{React-based User Dashboard and Frontend}}
\end{figure}

\section{Conclusion and Further Research}
\label{sec:orga131217}

@@

\section{References}
\label{sec:org5d12cd4}
